Supplementary Material for ``Evaluating infectious disease forecasts with allocation scoring rules''

### 2023-12-06 alloscore_manuscript/supplement.rnw
more painfully obtained iteration details

\usepackage{amsmath, amsfonts, amssymb, mathtools}
\usepackage{accents}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{cases}
\usepackage{caption}
\usepackage{soul}
\usepackage{pgfplots}
\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument{alloscore-application}

@@

Otherwise, by evaluating $TQ_F$ at $\tau_M = \frac{1}{2}\left(\tau_L + \tau_U\right)$ we can replace $I_1$ with the interval
\begin{align}
I_2 = 
\begin{cases}
[\tau_L, \tau_M] & \text{ if } K < q^{-}_{F_T,\tau_M} \\
[\tau_M, \tau_U] & \text{ if } K \geq q^{-}_{F_T,\tau_M}.
\end{cases}
\end{align}

Iterating this process we obtain a sequence $\{I_k\}, k=1,2,\ldots$ of intervals of widths 
$\left|I_k \right| = 2^{1-k}\left|I_1 \right|$ which either terminates at one of the scenarios 
($\bullet$), ($\bullet\!-$), or ($-\!\bullet$), or provides infinite sequences $\{\tau_{L,k}\}$ and $\{\tau_{U,k}\}$ converging
to $\tau^{\star}$ from below and above.

In the generic case of an infinite $\{I_k\}$, we need to define practical stopping criteria for each of three possible behaviours of 
$F_T$ at $K$:
\begin{samepage}
\begin{itemize}
\item[($\,\mathrlap{\,\bullet}{\diagup}\,$)] $\tau^{\star} = F_T(K-)$ and $TQ_F(\tau^{\star}) = \{K\}$ (that is, if $F_T$ is continuous and strictly increasing at $K$)
\item[(\raisebox{-.5ex}{$-$}\!\!\raisebox{.5ex}{$\bullet\!-$})] $F_T$ has a point mass at $K$
\item[($-\!\!\!\bullet\!\!\!-$)] $K \in (q^{-}_{F_T,\tau^{\star}}, q^{+}_{F_T,\tau^{\star}})$ (that is, all component forecasts $F_i$ have zero density at points $x_i \in (q^{-}_{F_i,\tau^{\star}}, q^{+}_{F_i,\tau^{\star}})$ and $\sum x_i = K$).
\end{itemize}
\end{samepage}

>>>>

\usepackage{amsmath, amsfonts, amssymb, mathtools}
\usepackage{accents}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{cases}
\usepackage{caption}
\usepackage{soul}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument{alloscore-application}

@@

Otherwise, by evaluating $TQ_F$ at $\tau_M = \frac{1}{2}\left(\tau_L + \tau_U\right)$ we can replace $I_1$ with one of its 
halves
\begin{align}
I_2 = 
\begin{cases}
[\tau_L, \tau_M] & \text{ if } K < q^{-}_{F_T,\tau_M} \\
[\tau_M, \tau_U] & \text{ if } K \geq q^{-}_{F_T,\tau_M}
\end{cases}
\end{align}
which also contains $\tau^{\star} = F_T(K)$. This follows from the definition $q^{-}_{F_T,\tau_M} := \min\{x \mid F_T(x) \geq \tau_M\}$, 
according to which
\begin{align}
\begin{cases}
K < q^{-}_{F_T,\tau_M} \text{ implies } \tau^{\star} = F_T(K) < \tau_M  \\
K \geq q^{-}_{F_T,\tau_M} \text{ implies } \tau^{\star} = F_T(K) \geq \tau_M.
\end{cases}
\end{align}

Iterating this process we obtain a sequence $\{I_k\}, k=1,2,\ldots$ of intervals of widths 
$\left|I_k \right| = 2^{1-k}\left|I_1 \right|$ which either terminates at one of the scenarios 
($\bullet$), ($\bullet\!-$), or ($-\!\bullet$), or provides infinite sequences $\{\tau_{L,k}\}$ and $\{\tau_{U,k}\}$ converging
to $\tau^{\star}$ from below and above. Note that this algorithm is somewhat more delicate than the usual ``bisection'' algorithm which
would involve bisecting intervals in the domain of $F_T$ to find a root.

In the generic case of an infinite $\{I_k\}$, we need to define practical stopping criteria for the possible limit behaviours of 
$F_T(K \pm \varepsilon)$ as $\varepsilon \searrow 0$:
\begin{itemize}
\item[($\mathrlap{\,\bullet}{\,/}\,$)] $F_T(K - \varepsilon) < F_T(K-) = F_T(K) < F_T(K + \varepsilon)$
(so that $\tau^{\star} = F_T(K-)$ and $TQ_F(\tau^{\star}) = \{K\}$)
\item[($/\!\!\raisebox{.9ex}{$\bullet$\!-}$)] $F_T(K - \varepsilon) < F_T(K-) = F_T(K) = F_T(K + \varepsilon)$
\item[($\raisebox{-.9ex}{-\!$\bullet$}\!\!/$)] $F_T(K - \varepsilon) = F_T(K) < F_T(K + \varepsilon)$
\item[($\raisebox{-.9ex}{\phantom{-}\!$\bullet$}\!\!/$)] $F_T(K - \varepsilon) \leq F_T(K-) < F_T(K) < F_T(K + \varepsilon)$
\item[($\,\bullet\!\text{-}$)] $F_T(K - \varepsilon) \leq F_T(K-) < F_T(K) = F_T(K + \varepsilon)$
\item[($\text{-}\!\!\bullet\!\!\text{-}$)]  $F_T(K - \varepsilon) = F_T(K) = F_T(K + \varepsilon)$
so that $K \in (q^{-}_{F_T,\tau^{\star}}, q^{+}_{F_T,\tau^{\star}})$ and all component forecasts $F_i$ have 
zero density at points $x_i \in (q^{-}_{F_i,\tau^{\star}}, q^{+}_{F_i,\tau^{\star}})$ and $\sum x_i = K$.
\end{itemize}

We also want to be able to decribe what further ``post-processing'' steps are required to find a sufficiently good approximation
to a Bayes act within the set
$\undertilde{\bm{F}}^{-1}(I_{\overline{k}})$ where $I_{\overline{k}}$ is the terminal search interval for $\tau^{\star}$.
